A {practical} review on linear and nonlinear global approaches to stability analysis

### 2018-06-08 ARTICLE_STABFEM/ARTICLE_ASME_V2.tex
D40:DAVID, il manque ligne 199 sur AdaptMode.edp sur votre fork. J'ai ajouté aussi plus de chiffres signif. sur le tableau WNL
D43: Update article

%%% use twocolumn and 10pt options with the asme2ej format
\documentclass[twocolumn,10pt]{asme2ej}

\usepackage{epsfig} %% for loading postscript figures
\usepackage{amsmath}

@@

We start from the general problem of a flow field $[{\bf u},p]$ satisfying the incompressible Navier-Stokes equations on a domain $\Omega$,
\begin{eqnarray} \label{NSprimitive}
\partial_t {\bf u} = {\cal NS} ({\bf u};p)
\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u})  \\
\nabla \cdot {\bf u} = 0,
\end{eqnarray}

with suitable boundary conditions on the frontier $\partial \Omega$ of the domain.
Here $ {\mathsf{D}}({\bf u}) $ is the rate-of-strain tensor defined as
$$
 {\mathsf{D}}({\bf u}) = 1/2
\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right)
$$ 
In the framework of finite element methods, we need to write the equation in weak form.
Prior to this we define a scalar product as follows, for either scalar or vectorial quantities 
$\left< \phi_1, \phi_2 \right> $:
$$
\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \Omega
$$
The weak form of the Navier-Stokes equations is readily defined by introducing test functions 
$[{\bf v},q]$ associated with the momentum and continuity equations, and integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions. Details on way boundary conditions can be incorporated in the weak formulation through integration by parts can be found in the appendix.}

\be{NSweak}
\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\cal NS} ({\bf u};p) \right> + \left< q, \nabla \cdot {\bf u}\right>.
\ee

@@

We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
${\cal NS} ({\bf u}_b,p_b) = 0$.
Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
\be{Newton1}
[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b].
\ee
Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and developing up to linear terms in terms of the perturbation lead to  
${\cal NS}  ({\bf u}_b^g,p_b^g) + {\cal L} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b;{\bf u}_b^g)$, which can also be written in weak form as :
%\be
%{\cal C}( {\bf u}_b^g , \delta {\bf u}_b) -\nabla \delta p_b 
%-2 \nu \nabla  {\bf D}(\delta {\bf u}_b)
%+
%\left[{\bf u}_b^g \cdot \nabla {\bf u}_b^g - \nabla p_b^g -2 \nu {\bf D}(\delta {\bf u}_b^g) \right]
% \qquad \mbox{with} \nabla \delta {\bf u} = 0. 
%\ee
%Or equivalently, in weak form :
\bes{Newton2}
&\left< {\bf v}, {\cal NS} ({\bf u}_b^g)\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
\\
+ &\left< { \bf v}, {\cal L} _{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b; {\bf u}_b^g) \right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0,
\ees
where ${\cal L}$ is the linearised Navier-Stokes operator, defined by its action on a flow field $({\bf u} ; p)$ as follows 
\be{defNSL}
 {\cal L}_{{\bf U}}( {\bf u}, p; {\bf U}) = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
+\frac{2}{Re} \nabla  \cdot {\mathsf{D}}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
 \ee
and ${\cal C}$ is the convection operator defined by 
\be{defC}
{\cal C}( {\bf U} , {\bf u}) = \left( {\bf U} \cdot \nabla \right) {\bf u} + \left( {\bf u} \cdot \nabla \right)  {\bf U}.
\ee

This problem can now be discretized by projecting upon a basis of Taylor-Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements. Noting $\delta X$ the discretization of ($\delta {\bf u}_b;\delta p_b$) this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
In our implementation, the algorithm is written in the Freefem++ solver {\em Newton\_2D.edp} 
which is wrapped by the Matlab driver {\em Freefem\_BaseFlow.m}.

@@

\be{startmodepropre}
{\bf u} ({\bf{x}},t) = {\bf u}_b({\bf{x}}) + \epsilon \hat{\bf u}({\bf{x}}) e^{\lambda t}, \,\,\,\, {p}({\bf{x}},t) = {p}_b({\bf{x}}) + \epsilon \hat{p}({\bf{x}}) e^{\lambda t}
\ee
where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
$\omega$ the oscillation rate, $\hat{{\bf u}},\hat{p}$ the eigenmodes, and $\epsilon$ a small parameter.
The eigenmodes and the eigenvalues are the solution of the following eigenproblem:

\be{LEP}
\lambda \hat{{\bf u}} = {\cal L}_{{\bf u}_b}( \hat{\bf u},\hat{p}),
\ee
or, in weak form : 
\be{eigenvalueproblem}
\lambda \left< {\bf v} , \hat{{\bf u}} \right> = \left< {\bf v}, {\cal L}_{{\bf u}_b} ( \hat{\bf u},\hat{p})\right> + \left< q, \nabla \cdot \hat{\bf u} \right>.
\ee
After discretization, we end up with an eigenvalue problem with the matricial form
\be{Eigen_matricial}
\lambda {\mathsf{B}} \hat{X} = {\mathsf{A}} \hat{X}
\ee
Where ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal L}_{{\bf u}_b}$, i.e. the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.

@@

\be{drag}
D = F_x ({\bf u},p) = 
 \int_{\Gamma_{cil}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} d\ell
\ee

@@

In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as {\color{red}$\partial_t {\bf u} = {\cal NS} ({\bf u})$}, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field.

In the nonlinear r{\color{red}e}gime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
Instead, {\color{red} we taken the Reynolds decomposition ${\bf q}={\bf q}_m({\bf x})+{\bf q}'({\bf x},t)$, with ${\bf q}'$ the nonlinear perturbation and ${\bf q}_m$ the {\em mean flow} defined as the time-average  of the flow:}
\be{defumean}
{\bf q}_m({\bf x})  = \frac{1}{T} \int_0^{T}  {\bf q}({\bf x},t)  dt,
\ee
where $T = 2\pi/\omega$  is the period of the oscillation cycle.

@@

Another quantity which has been particularly addressed in previous studies is the mean recirculation length $L_x$
already discussed{\color{red},} introduced and documented in figure {\color{red}??}. {\color{red} However, in a} nonlinear regime, the recirculation bubble becomes unsteady, {\color{red} becoming} difficult to define properly an instantaneous recirculation length. It is still possible to define a mean recirculation length associated to the mean flow. %On va le faire ??

In the next sections we will document the predictions of the WNL and SC models regarding the quantities $A_E$ and $L_x$ adopted in past studies. In addition, we will document two other quantities of practical interest : the Drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder. 
Both are periodic functions of time and{\color{red},} owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics:{\color{red}
\be{drag_lift_def}
\begin{cases}
F_x=F_{x,0} + \sum_{n=1}^\infty \big( F_{x,2n,c} \cos ( 2 n \omega t) + F_{x,2n,s} \sin( 2 n  \omega t ) \big) \\
\begin{split}
F_y  =  \sum_{n=1}^\infty \big(  F_{y,{2n-1},c} \cos ((2n-1) \omega t ) +\\
 F_{y,(2n-1),s} \sin ((2n-1) \omega t) \big)
\end{split}
\end{cases}.
\ee

In the sequel we will focus on the {\em mean drag}  $F_{x,0}$ and on the fundamental frequency part of the drag and lift given by $F_{x,2,c}$, $F_{x,2,s}$ and $F_{y,1,c}$, $F_{y,1,s}$.
 }

@@

We give here a brief account of the weakly nonlinear model of Sipp \& 
Lebedev\cite{SippLebedev}, also discussed by Gallaire et al. \cite{FDR2016}. 
The derivation is based on a multiple scale  decomposition based on the parameter {\color{red}$\epsilon^2 = 1/Re_c - 1/Re$}. 
In the case where we are interested only in the {\color{red}description} of the saturation cycle, the starting point can be taken as the following expansion of the state-vector ${\bf{q}}=({\bf{u}},p)$ defining the flow:
\be{WNL1}
\begin{aligned}
&{\bf q} = {}  {\bf q}_{bc} + \epsilon \left[ A_{wnl}  \hat{\bf q} e^{i (\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right]\\
&+ \epsilon^2 \left[ {\bf q}_\epsilon + |A_{wnl}|^2  {\bf q}_{2,0} + \left(  A_{wnl}^2 {\bf q}_{2,2} e^{2 i(\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right) \right]\\
& + {\cal O}( \epsilon ^3),
\end{aligned}
\ee
where ${\bf q}_{bc}$ is the base flow at the threshold $Re_c$, $\hat{\bf q}$ the neutral 
eigenmode at $Re_c$, {\color{red} $A_{wnl}$ an amplitude,} $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency, {\color{red} ${\bf q}_{\epsilon}$ the base flow modifications related to the increase of $\epsilon$, ${\bf q}_{2,0}$ the flow response to the steady nonlinear interactions of $\hat{\bf q}$ with its conjugate, ${\bf q}_{2,2}$ the flow response to the unsteady nonlinear interactions of $\hat{\bf q}$ with itself and  ${\cal O}( \epsilon ^3)$ the third order terms.   }

@@

where the subscripts $r$ and $i$ represent the real and imaginary parts.
}
{\color{red}
Recasting equation \ref{WNL1} in the {\em mean flow} definition \ref{defumean}, we obtain
\be{mean_flow_WNL}
{\bf q}_m({\bf x })= {\bf q}_{bc}+\epsilon^2 {\bf q}_\epsilon + |A|^2{\bf q}_{2,0},
\ee
where the first two terms give the base flow approximation at the $Re$ prescribed by $\epsilon$. }

{\color{red} Finally, the associated Drag and Lift are given respectively by:
\be{drag_cos}
\begin{aligned}
F_{x,WNL} = F_{x}({\bf q}_{bc})&+\epsilon^2 \big( 
F_{x}({\bf q}_{\epsilon})- 2\mathsf{D}({\bf u}_{bc}).{\bf n}_x \big)\\
&+|A|^2 F_{x}({\bf q}_{2,0})\\
&+2|A|^2\big(F_{x,r}({\bf q}_{2,2})\cos(2\omega t)
-F_{x,i}({\bf q}_{2,2})\sin(2\omega t) \big),
\end{aligned}
\ee
\be{lift_cos}
\begin{aligned}
F_{y,WNL} =2\big(|A|_r F_{x,r}({\bf \hat{q}})\cos(\omega t)-
|A|_i F_{x,i}({\bf \hat{q}})\sin(\omega t) \big),\\
\end{aligned}
\ee
where $F_{x}$ and $F_{y}$ are given by \ref{drag} and \ref{lift}, respectively. All terms in these equations can be matched with the interesting ones in \ref{drag_lift_def}: $F_{x,0}$ is the first 4 terms of \ref{drag_cos}; $F_{x,2,c}$, $F_{x,2,s}$ are the fifth and sixth terms of \ref{drag_cos}; $F_{y,1,c}$, $F_{y,1,s}$ are the first and second terms of \ref{lift_cos}. We note that the \textit{sine} term is associated to the phase of the forces in a physical way. }

@@

{\color{blue}
A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice of the eigenmodes{\color{red}, as pointed before}. Several choices are possible. In the literature three possibilities have been used:
\begin{itemize}
\item First, \cite{SippLebedev} normalized the eigenmode by assuming a specified value to the $y$-component of the velocity at one point, namely:
\be{normsipp}
\hat{u_y}(1,0) = 0.4612.
\ee
The advantage of this choice is that the amplitude ${\color{red}|A|}$ is then a measure of the energy of the perturbation: 
${\color{red}|A|} \approx A_E$. {\color{red}However the lift phase its not fixed.}

\item Secondly, \cite{FDR2016} proposed the following {\color{red}normalization} choice:
\be{normFDR}
\int_\Omega |\hat{\bf u}|^2 d {\bf x}  = \frac{1}{2}.
\ee
This directly leads to ${\color{red}|A|} = A_E$.{\color{red} The lift phase is not specified in \cite{FDR2016} and can be set to nil before the normalization.}

\item Thirdly, following \cite{Fabre2012}, another convenient choice is to normalize the eigenmode with its lift 
force: 
\be{normfabre}
{\color{red}F_y(\hat{\bf q}) }={\color{red} \frac{1}{2}}.
\ee
The advantage of this choice is that the amplitude ${\color{red}|A|}$ is directly related to the fundamental lift:
\be{lift_explanation}
F_{y,1,c} 
= {\color{red}|A|} \left( {\color{red}\frac{1}{2}} e^{i \omega t} + c.c. \right)
=   {\color{red}|A|} \cos (\omega t) ; \quad F_{y,1,{\color{red}s}} = 0. 
\ee

@@

{\color{red}
In our implementation of the WNL approach, we allowed to choose the normalization convention, as seen in line 3 of figure \ref{fig:listingNL}.
%%ATTENTION, si figure est actualisé, il faut actualiser la ligne
In table \ref{tab:WNL_coefs} we give the predictions of the WNL approach using the three normalization choices.
We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice. On the other hand, the frequency deviation $\omega_\epsilon$ and the $\lambda$ coefficient, as well as the drag and lift coefficients are independent of it.
%On the other hand, the frequency deviation as well as the drag and lift coefficients are independent of it.
}
\begin{table*}[!h]
\centering
$$
\begin{array}{|c||c|c|c|c|c|c|c|}
\hline
\mbox{Norm.} & \lambda & \nu_{0} & \nu_{2} &\omega_{\epsilon}(rad/s)&F_{x,0}&|F_{x,2}|&|F_{y,1}|\\%& F_{y,1}
\hline
\mbox{\cite{SippLebedev}} & 9.1+3.3i & 9.4-32.1i & -0.3-0.9i & 36.2
&0.71+5.3\epsilon^2&0.032\epsilon^2&0.54\epsilon\\
\mbox{\cite{FDR2016}} & 9.1+3.3i  & 4.9\times 10^{-4}-1.7\times 10^{-3}i & -1.6\times 10^{-5}-4.5\times 10^{-5}i &36.2&
0.71+5.3\epsilon^2&0.032\epsilon^2&0.54\epsilon \\
\mbox{\cite{Fabre2012}} & 9.1+3.3i & 32.6-111.2i & -1.1-3.0i & 36.2
&0.71+5.3\epsilon^2&0.032\epsilon^2&0.54\epsilon\\
\hline
\end{array}
$$
\caption{Coefficients of the weakly nonlinear approach }
\label{tab:WNL_coefs}
\end{table*}

>>>>

%%% use twocolumn and 10pt options with the asme2ej format

\documentclass[twocolumn,10pt]{asme2ej}

\usepackage[none]{hyphenat}
\usepackage{epsfig} %% for loading postscript figures
\usepackage{amsmath}

\usepackage{breqn}

@@

We start from the general problem of a flow field $[{\bf u},p]$ satisfying the incompressible Navier-Stokes equations on a domain $\Omega$,
\begin{eqnarray} \label{NSprimitive}
\partial_t {\bf u} = {\color{red}{\cal NS} ({\bf u},p)}
\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u}),  \\
\nabla \cdot {\bf u} = 0,
\end{eqnarray}

with suitable boundary conditions on the frontier $\partial \Omega$ of the domain.
Here $ {\mathsf{D}}({\bf u}) $ is the rate-of-strain tensor defined as
$$
 {\mathsf{D}}({\bf u}) = 1/2
\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right),
$$ 
In the framework of finite element methods, we need to write the equation in weak form.
Prior to this we define a scalar product as follows, for either scalar or vectorial quantities 
$\left< \phi_1, \phi_2 \right> $:
$$
\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \Omega,
$$
The weak form of the Navier-Stokes equations is readily defined by introducing test functions 
$[{\bf v},q]$ associated with the momentum and continuity equations, and integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions. Details on way boundary conditions can be incorporated in the weak formulation through integration by parts can be found in the appendix.}

\be{NSweak}
\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\color{red}{\cal NS} ({\bf u},p)} \right> + \left< q, \nabla \cdot {\bf u}\right>.
\ee

@@

We look for a steady base-flow {\color{red}$[{\bf u}_b,p_b]$} satisfying the steady Navier-Stokes equations, i.e. 
%${\cal NS} ({\bf u}_b,p_b) = 0$.
{\color{red}${\cal NS} ({\bf u}_b,p_b) = 0$.}
Suppose that we have a {\color{red}``guess''}  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
\be{Newton1}
[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b].
\ee
Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and developing up to linear terms in terms of the perturbation lead to  
${\cal NS}  ({\bf u}_b^g,p_b^g) + {\color{red} {\cal L} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)}$, which can also be written in weak form as :
%\be
%{\cal C}( {\bf u}_b^g , \delta {\bf u}_b) -\nabla \delta p_b 
%-2 \nu \nabla  {\bf D}(\delta {\bf u}_b)
%+
%\left[{\bf u}_b^g \cdot \nabla {\bf u}_b^g - \nabla p_b^g -2 \nu {\bf D}(\delta {\bf u}_b^g) \right]
% \qquad \mbox{with} \nabla \delta {\bf u} = 0. 
%\ee
%Or equivalently, in weak form :
\bes{Newton2}
&\left< {\bf v}, {\color{red}{\cal NS} ({\bf u}_b^g,p_b^g)}\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
\\
+ &\left< { \bf v}, {\color{red}{\cal L} _{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b) }\right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0,
\ees
where ${\cal L}$ is the linearised Navier-Stokes operator, defined by its action on a flow field {\color{red}$[{\bf u} , p]$} as follows 
\be{defNSL}
{\color{red} {\cal L}_{{\bf U}}( {\bf u}, p)} = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
+\frac{2}{Re} \nabla  \cdot {\mathsf{D}}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
 \ee
and ${\cal C}$ is the convection operator defined by 
\be{defC}
{\cal C}( {\bf U} , {\bf u}) = \left( {\bf U} \cdot \nabla \right) {\bf u} + \left( {\bf u} \cdot \nabla \right)  {\bf U}.
\ee

This problem can now be discretized by projecting upon a basis of Taylor-Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements. Noting $\delta X$ the discretization of {\color{red}$[\delta {\bf u}_b,\delta p_b]$} this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
In our implementation, the algorithm is written in the Freefem++ solver {\em Newton\_2D.edp} 
which is wrapped by the Matlab driver {\em Freefem\_BaseFlow.m}.

@@

\be{startmodepropre}
{\bf u} ({\bf{x}},t) = {\bf u}_b({\bf{x}}) + \epsilon \hat{\bf u}({\bf{x}}) e^{\lambda t}, \,\,\,\, {p}({\bf{x}},t) = {p}_b({\bf{x}}) + \epsilon \hat{p}({\bf{x}}) e^{\lambda t},
\ee
where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
$\omega$ the oscillation rate, $\hat{{\bf u}},\hat{p}$ the eigenmodes, and $\epsilon$ a small parameter.
The eigenmodes and the eigenvalues are the solution of the following eigenproblem:

\be{LEP}
\lambda \hat{{\bf u}} = {\cal L}_{{\bf u}_b}( \hat{\bf u},\hat{p}),
\ee
or, in weak form : 
\be{eigenvalueproblem}
\lambda \left< {\bf v} , \hat{{\bf u}} \right> = \left< {\bf v}, {\cal L}_{{\bf u}_b} ( \hat{\bf u},\hat{p})\right> + \left< q, \nabla \cdot \hat{\bf u} \right>.
\ee
After discretization, we end up with an eigenvalue problem with the matricial form
\be{Eigen_matricial}
\lambda {\mathsf{B}} \hat{X} = {\mathsf{A}} \hat{X},
\ee
{\color{red} where} ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal L}_{{\bf u}_b}$, i.e. the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.

@@

\be{drag}
D = F_x ({\bf u},p) = 
 \int_{\Gamma_{cil}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} d\ell,
\ee

@@

In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as {\color{red}$\partial_t {\bf u} = {\cal NS} ({\bf u})$}, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field. {\color{red} The same is done with the linearised operator ${\cal L}_{{\bf U}}( {\bf u})$.}

In the nonlinear r{\color{red}e}gime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
Instead, {\color{red} we taken the Reynolds decomposition ${\bf u}={\bf u}_m({\bf x})+{\bf u}'({\bf x},t)$, with ${\bf u}'$ the nonlinear perturbation and ${\bf u}_m$ the {\em mean flow} defined as the time-average  of the flow:}
\be{defumean}
{\bf u}_m({\bf x})  = \frac{1}{T} \int_0^{T}  {\bf u}({\bf x},t)  dt,
\ee
where $T = 2\pi/\omega$  is the period of the oscillation cycle.

@@

Another quantity which has been particularly addressed in previous studies is the mean recirculation length $L_x$
already discussed{\color{red},} introduced and {\color{red}documented in figure \ref{fig:LxandDrag}}. {\color{red} However, in a} nonlinear regime, the recirculation bubble becomes unsteady, {\color{red} becoming} difficult to define properly an instantaneous recirculation length. It is still possible to define a mean recirculation length associated to the mean flow. %On va le faire ??

In the next sections we will document the predictions of the WNL and SC models regarding the quantities $A_E$ and $L_x$ adopted in past studies. In addition, we will document two other quantities of practical interest : the Drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder. 
Both are periodic functions of time and{\color{red},} owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics:{\color{red}
%\be{drag_lift_def}
%\begin{cases}
%F_x=F_{x,0} + \sum_{n=1}^\infty \big( F_{x,2n,c} \cos ( 2 n \omega t) + F_{x,2n,s} \sin( 2 n  \omega t ) \big) \\
%\begin{split}
%F_y  =  \sum_{n=1}^\infty \big(  F_{y,{2n-1},c} \cos ((2n-1) \omega t ) +\\
% F_{y,(2n-1),s} \sin ((2n-1) \omega t) \big)
%\end{split}
%\end{cases}.
%\ee
\begin{align}
F_x &=F_{x,0} + \sum_{n=1}^\infty \big( F_{x,2n,c} \cos ( 2 n \omega t) + F_{x,2n,s} \sin( 2 n  \omega t ) \big),
\\
\begin{split}
F_y  & =\sum_{n=1}^\infty \big( F_{y,{2n-1},c} \cos ((2n-1) \omega t )\\
             &\qquad + F_{y,(2n-1),s}  \sin ((2n-1) \omega t) \big).
\end{split}
\label{drag_lift_def}
\end{align}

In the sequel we will focus on the {\em mean drag}  $F_{x,0}$ and on the fundamental frequency part of the lift given by $F_{y,1,c}$ and $F_{y,1,s}$.
 }

@@

We give here a brief account of the weakly nonlinear model of Sipp \& 
Lebedev\cite{SippLebedev}, also discussed by Gallaire et al. \cite{FDR2016}. 
The derivation is based on a multiple scale  decomposition based on the parameter {\color{red}$\epsilon^2 = 1/Re_c - 1/Re$}. 
In the case where we are interested only in the {\color{red}description} of the saturation cycle, the starting point can be taken as the following expansion of %the state-vector ${\bf{q}}=({\bf{u}},p)$ defining the flow:
 {\color{red}the velocity flow field:} 
 {\color{red}
\be{WNL1}
\begin{aligned}
&{\bf u} = {}  {\bf u}_{bc} + \epsilon \left[ A_{wnl}  \hat{\bf u} e^{i (\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right]\\
&+ \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i(\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right) \right]\\
& + {\cal O}( \epsilon ^3),
\end{aligned}
\ee
}
where {\color{red}${\bf u}_{bc}$} is the base flow at the threshold $Re_c$, {\color{red} $\hat{\bf u}$} the neutral 
eigenmode at $Re_c$, {\color{red} $A_{wnl}$ an amplitude,} $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency, {\color{red} ${\bf u}_{\epsilon}$ the base flow modifications related to the increase of $\epsilon$, ${\bf u}_{2,0}$ the flow response to the steady nonlinear interactions of $\hat{\bf u}$ with its conjugate, ${\bf u}_{2,2}$ the flow response to the unsteady nonlinear interactions of $\hat{\bf u}$ with itself and  ${\cal O}( \epsilon ^3)$ the third order terms.   }

@@

where the subscripts $r$ and $i$ represent the real and imaginary parts.
}
{\color{red}
Recasting equation \ref{WNL1} in the {\em mean flow} definition \ref{defumean}, we obtain
\be{mean_flow_WNL}
{\bf u}_m({\bf x })= {\bf u}_{bc}+\epsilon^2 {\bf u}_\epsilon + |A|^2{\bf u}_{2,0},
\ee
where the first two terms give the base flow approximation at the $Re$ prescribed by $\epsilon$. }

{\color{red} Finally, the associated Drag and Lift are given respectively by:
\be{drag_cos}
\begin{aligned}
F_{x,WNL} = F_{x}({\bf u}_{bc})&+\epsilon^2 \big( 
F_{x}({\bf u}_{\epsilon})- 2\mathsf{D}({\bf u}_{bc}).{\bf n}_x \big)\\
&+|A|^2 F_{x}({\bf u}_{2,0})\\
&+2|A|^2\big(F_{x,r}({\bf u}_{2,2})\cos(2\omega t)
-F_{x,i}({\bf u}_{2,2})\sin(2\omega t) \big),
\end{aligned}
\ee
\be{lift_cos}
\begin{aligned}
F_{y,WNL} =2\big(|A|_r F_{x,r}({\bf \hat{u}})\cos(\omega t)-
|A|_i F_{x,i}({\bf \hat{u}})\sin(\omega t) \big),\\
\end{aligned}
\ee
where $F_{x}$ and $F_{y}$ are given by \ref{drag} and \ref{lift} (with the associated pressure field implicit), respectively . All terms in these equations can be matched with the interesting ones in \ref{drag_lift_def}: $F_{x,0}$ is the first 4 terms of \ref{drag_cos}; $F_{x,2,c}$, $F_{x,2,s}$ are the fifth and sixth terms of \ref{drag_cos}; $F_{y,1,c}$, $F_{y,1,s}$ are the first and second terms of \ref{lift_cos}. We note that the \textit{sin} term is associated to the phase of the forces in a physical way. }

@@

{\color{blue}
A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice of the eigenmodes{\color{red}, as pointed before}. Several choices are possible. In the literature three possibilities have been used:
\begin{itemize}
\item First, \cite{SippLebedev} normalized the eigenmode by assuming a specified value to the $y$-component of the velocity at one point, namely:
\be{normsipp}
{\color{red}\hat{u}}_y(1,0) = 0.4612.
\ee
The advantage of this choice is that the amplitude ${\color{red}|A|}$ is then a measure of the energy of the perturbation: 
${\color{red}|A|} \approx A_E$. {\color{red}However the lift phase its not fixed.}

\item Secondly, \cite{FDR2016} proposed the following {\color{red}normalization} choice:
\be{normFDR}
\int_\Omega |\hat{\bf u}|^2 d {\bf x}  = \frac{1}{2}.
\ee
This directly leads to ${\color{red}|A|} = A_E$. {\color{red} The lift phase is not specified in \cite{FDR2016} and can be set to nil before the normalization.}

\item Thirdly, following \cite{Fabre2012}, another convenient choice is to normalize the eigenmode with its lift 
force: 
\be{normfabre}
{\color{red}F_y(\hat{\bf u}) }={\color{red} \frac{1}{2}}.
\ee
The advantage of this choice is that the amplitude ${\color{red}|A|}$ is directly related to the fundamental lift:
\be{lift_explanation}
F_{y,1,c} 
= {\color{red}|A|} \left( {\color{red}\frac{1}{2}} e^{i \omega t} + c.c. \right)
=   {\color{red}|A|} \cos (\omega t) ; \quad F_{y,1,{\color{red}s}} = 0. 
\ee

@@

{\color{red}
In our implementation of the WNL approach, we allowed to choose the normalization convention, as seen in line 3 of figure \ref{fig:listingNL}.
%%ATTENTION, si figure est actualisé, il faut actualiser la ligne
In table \ref{tab:WNL_coefs} we give the predictions of the WNL approach using the three normalization choices.
We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice. On the other hand, the frequency deviation $\omega_\epsilon$ and the $\lambda$ coefficient, as well as the drag and lift coefficients are independent of it.
%On the other hand, the frequency deviation as well as the drag and lift coefficients are independent of it.
}
\begin{table*}[!h]
\centering
$$
\begin{array}{|c||c|c|c|c|c|c|c|}
\hline
\mbox{Norm.} & \lambda & \nu_{0} & \nu_{2} &\omega_{\epsilon}(rad/s)&F_{x,0}&|F_{x,2}|&|F_{y,1}|\\%& F_{y,1}
\hline
\mbox{\cite{SippLebedev}} & 9.10988 & 9.3996-32.0289i & -0.305116-0.866118i & 36.2307
&0.709469&0.0324441\epsilon^2&0.537254\epsilon\\
\mbox{\cite{FDR2016}} & +  & 4.88701\times 10^{-4}-1.66524\times 10^{-3}i & -1.58635\times 10^{-5}-4.50309\times 10^{-5}i &36.2307&
+&0.0324441\epsilon^2&0.537254\epsilon \\
\mbox{\cite{Fabre2012}} & 3.28004i & 32.62-111.152i & -1.05886-3.00574i & 36.2307
&5.2524\epsilon^2&0.0324441\epsilon^2&0.537254\epsilon\\
\hline
\end{array}
$$
\caption{Coefficients of the weakly nonlinear approach {\color{red} NB for D.Fabre: Columns 2 and 6 have the same value.}}
\label{tab:WNL_coefs}
\end{table*}

{\color{red} 
The forces coefficients given by $F_x({\bf u})$ and $F_y({\bf u})$ are then converted in a more traditional form, $C_x=2F_x({\bf u})$ and $C_y=2F_y({\bf u})$.
}
As can be seen on figure \ref{fig:HB_SC_DATA_COMP},  the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by Gallaire et al.? and also observed by Tchoufag et al. \cite{Tchoufag2015}, a convenient definition of the $\epsilon$ improves the results). {\color{red} These aspects are justified by the pertubative nature of the WNL approach. The description of the limit cycle can be extended to larger $Re$ with the approach presented next.  }
